 

### 2020-09-10 vertical-thermal-review.Rmd
Update vertical-thermal-review.Rmd

We’re seeing increasing evidence that this impacts the ecology, with potential feedbacks to climate change, especially in protecting cool-acclimated species (Suggitt et al. 2018, Scheffers et al. 2013, Defrenne et al. 2013). 
     - @zellweger_forest_2020 
     - (Suggitt et al. 2018, Scheffers et. al 2014)

>>>>

We're seeing increasing evidence that this impacts the ecology, with potential feedbacks to climate change, especially in protecting cool-acclimated species (Suggitt et al. 2018, Scheffers et al. 2013, Defrenne et al. 2013). 
     - @zellweger_forest_2020 
     - (Suggitt et al. 2018, Scheffers et. al 2014)
